---
output:
 html_document:
  toc: true
  toc_depth: 1
  toc_float:
   collapsed: false
---

```{r, child = 'cdtcsschunks.Rmd'}
```

<div id='toc-index' class='toc-index-class'>

# [CDT GUI](cdt_file_menu.html)

## [CDT Main Window](cdt_file_menu.html#cdt.main.win)

### [Menu Bar](cdt_file_menu.html#menu.bar)

### [Toolbars](cdt_file_menu.html#toolbars)

### [Open Files](cdt_file_menu.html#open.files)

### [Input and Command Panels](cdt_file_menu.html#cmd.panel)

### [Map and Table View](cdt_file_menu.html#map.view)

### [Output Message](cdt_file_menu.html#out.msg)

### [Status Bar](cdt_file_menu.html#status.bar)

# [CDT Input Data Format](cdt_data_input.html)

## [ Data format with several stations](cdt_data_input.html#cdt.format.data)

## [Input series for one station](cdt_data_input.html#cdt.ts.data)

## [Coordinates data](cdt_data_input.html#cdt.coords.data)

## [NetCDF data](cdt_data_input.html#cdt.ncdf.data)

## [NetCDF filename format](cdt_data_input.html#cdt.ncdf.ffrmt)

# [Format CDT Input data](format_cdt_data.html)

## [Multiple Files](format_cdt_data.html#multiple.files)

## [Single File](format_cdt_data.html#single.file)

## [Merge two CDT data format](format_cdt_data.html#merge.2cdt.data)

# [Assess Data Availability](assess_data_availability.html)

# [Aggregating Time Series](aggregate_TS.html)

# [Download data](download_data.html)

## [ Download satellite rainfall estimates  data (RFE)](download_data.html#down.rfe)

## [ Download Digital Elevation Model data (DEM)](download_data.html#down.dem)

## [ Download country boundary](download_data.html#down.shp)

# [Filling missing dekadal temperature values](fill_na_temp.html)

# [Merging Rainfall](merging_rainfall.html)

## [ Bias calculation](merging_rainfall.html#rr.calc.bias)

## [ Apply bias correction](merging_rainfall.html#rr.apply.bias)

## [ Compute Spatio-temporal Trend Coefficients](merging_rainfall.html#rr.calc.lmcoef)

## [ Merging Data](merging_rainfall.html#rr.merge.data)

# [Merging Temperatures](merging_temperature.html)

## [Compute Downscaling Coefficients](merging_temperature.html#tt.calc.dcoef)

## [Reanalysis Downscaling](merging_temperature.html#tt.downscale)

## [Bias calculation](merging_temperature.html#tt.calc.bias)

## [Apply bias correction](merging_temperature.html#tt.apply.bias)

## [Compute Spatio-temporal Trend Coefficients](merging_temperature.html#tt.calc.lmcoef)

## [Merging Data](merging_temperature.html#tt.merge.data)

# [Updating dekadal rainfall](update_dekadal_rainfall.html)

# [Validation](validation.html)

</div>

```{r, child = '_generated_date.Rmd'}
```
