---
title: "Aggregating Time Series"
output:
  html_document:
    toc: true
---

```{r, child = "cdtMenuToolbar.Rmd"}
```

The menu `r menuselection('Data Preparation','Aggregating Time Series')` allows you to convert a time series with a given time step to another time step. It will display a dialog box allowing you to enter the input data and set the required parameters.

`r put.image("images/data_prepraration/aggregate_ts/aggreagate_TS.png", height = 50, width = 50)`

1. Select the time step of your input time series. There are three choices available: daily, dekadal and monthly data.
2. Select the time step to aggregate the time series. There are 5 possible time steps for the outputs:
	* 'Dekadal data'
	* 'Monthly data'
	* 'Yearly data'
	* 'Seasonal data': a seasonal time series is a series defined for a specific season (over a given months). For example, December-January-February (DJF), June-July-August (JJA) or May-October (MJJASO) for six-month seasonal series. 
	* 'Rolling Seasonal data': a rolling seasonal time series is a seasonal time series which includes all possible seasons over the year. For example, for three-month seasonal series, the series will be composed of the 12 possible seasons (DJF, JFM, FMA, MAM, AMJ, MJJ, JJA, JAS, ASO, SON, OND, NDJ)
3. Enter here the start month of the season (1 to 12).
4. Enter here the length of the season. For example, 3 for three-month (DJF) and 6 for six-month length (MJJASO).
5. Select the type of data to be aggregated. There are three choices available: `One station series`, `CDT data format` and `NetCDF gridded data`. The case of `One station series` and `NetCDF gridded data` are described in more detail in the sections below.
6. Select the function to be used to aggregate the series. For temperature, select `mean` and `sum` for precipitation.
7. Enter the minimum fraction of non-missing values that must be present within each output time step. If the fraction of non-missing values within the output time step is less than this fraction a missing value is returned.
8. In the case of `One station series` and `CDT data format`, select the file containing the station data,  and for `NetCDF gridded data`, enter the full path to directory containing the NetCDF data,  or use `r button('...')` to browse it.
9. In the case of `One station series` and `CDT data format`, enter the name of the file or the full path of the file to save the aggregated data. For `NetCDF gridded data`, enter the full path to directory to save result.

Click on the button ![][executetask] to aggregate the data. 

__*One station series*__

If you select `One station series` for the type of data, the button `r button('Settings')` will be enabled allowing you to set the options for the format of data

`r put.image("images/data_prepraration/aggregate_ts/one_stn_format.png", height = 40, width = 40)`

 >  Go to the section [Input series for one station](cdt_data_input.html#cdt.ts.data) for more details on the format of the data and the date.

1. Choose the number of climate variables in the file.
2. Choose the format of date (grouped or separated).

__*NetCDF gridded data*__

By selecting `NetCDF gridded data`, the button `r button('Settings')` will be enabled which allows you to edit the date range of the series to be aggregated and the format of the file names for the ncdf input and output files.

`r put.image("images/data_prepraration/aggregate_ts/ncdf_params.png", height = 60, width = 60)`

1. Enter the date range of the series you want to aggregate, make sure the date is valid, meaning that dates like 2016-06-31 and 2015-02-29 will throw an error.
2. Enter the filename format of the input netcdf files
3. Enter the filename format of the output netcdf files

>  Go to the section [NetCDF filename format](cdt_data_input.html#cdt.ncdf.ffrmt) for more details on the format of the NetCDF file names.

Click on the button ![][executetask] to aggregate the data. 
<!-- 
```{r, child = "_generated_date.Rmd"}
```
-->