---
title: "Assess Data Availability"
output:
  html_document:
    toc: true
---

```{r, child = "cdtMenuToolbar.Rmd"}
```

The menu `r menuselection('Data Preparation','Assess Data Availability')` provides a summary view of your data. It gives an informative graphics of the available observations and the proportion of missing values in the data. 

`r put.image("images/data_prepraration/assess_data/asses_data_availab.png", height = 60, width = 60)`

1. Select the time step of your data, there are three choices available: daily, dekadal and monthly data.
2. Select the file containing the station data, if the file is not loaded yet and therefore not listed, use the button `r button('...')` to open it.
3. Click `r button('Distance-Correlation')` to see the plot of correlation as a function of distance. The plot summarizes the spatial correlations for each station pair plotted against the corresponding inter-station distance.
`r put.image("images/data_prepraration/assess_data/dist_cor.png", height = 60, width = 60)`
4. Click `r button('Miss.Data Summary')` to have a plot summary of the available data: the number of working stations and the proportion of missing observations.
 `r put.image("images/data_prepraration/assess_data/funct_stn.png", height = 60, width = 60)`
5. Select a station from drop-down combo box to get a plot of the available data per year during the operating period of the station. You can use  `r button('<<')` and `r button('>>')` to easily switch between stations.
 `r put.image("images/data_prepraration/assess_data/miss_summary.png", height = 60, width = 60)`

<!-- 
```{r, child="_generated_date.Rmd"}
```
 -->