---
title: "CDT File menu"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.path='images/R_images/cdt_file_menu.')
```

```{r, child="cdtMenuToolbar.Rmd"}
```


This is a reference ![image][executetask] with multimarkdown attributes.



test fonc `r menuselection('rija faniriantsoa',nata,ranto,ando)`


## GUI Conventions

This section describes the uniform styles that will be used throughout this manual.

* Menu Options: `r menuselection('rija faniriantsoa',nata,ranto,ando)`
* Toolbar icons: ![][redrawplot0]
* Toolbar icons: ![][redrawplot1]

* button: `r button(Cancel)`
* browse: `r button('...')`
* Tabs: `r onglet(Options)`
* drop down list button: `r dropdownlistBut()`
* checkbox: `r checkbox('Use elevation')`
* radio button:  `r radiobutton('Use elevation')`
* dropdown list: This ![][dropdownarrow] a listbox
* Select a number: ![][spinbox]
* Browse for a file: ![][browsebutf]

* Zoom in non active: ![][zoomin0]
* Zoom in active: ![][zoomin1]

* Redraw map non active: ![][redrawmap0]
* Redraw map  active: ![][redrawmap1]


```{r, child="_generated_date.Rmd"}
```

